---
title: "Quiz3"
author: "Dinh Tuan Phan"
date: "4/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1

Download data

```{r}

download.file('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv', destfile = 'ACS.csv', method='curl')

```
Read data into data.frame

```{r}
ACS <- read.csv('ACS.csv')

agricultureLogical <- ACS$ACR == 3 & ACS$AGS == 6
```

Answer:
```{r}
head(which(agricultureLogical), 3)
```

## Question 2

First, you need to install package 'jpeg' if you have not done so.

Load the package:

```{r}
library(jpeg)
```

Download file:
```{r}

download.file('https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg', destfile = 'jeff.jpg', mode='wb' )
```

Read the image:

```{r}
picture <- jpeg::readJPEG('jeff.jpg', native=TRUE)
```

Get the quantiles and Answers:
```{r}

quantile(picture,probs = c(0.3,0.8))

```
## Question 3
First, you need to install package 'data.table' if you have not done so.

Load the package:
```{r}
library(data.table)
```
Download GDP data
```{r}
GDP <- data.table::fread('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv', skip = 4, nrows = 190, select = c(1,2,4,5), col.names = c('CountryCode','Rank','Economy','Total'))
```
Download EDU data

```{r}
EDU <- data.table::fread('https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv')
```
Match data

```{r}
mergedDT <- merge(GDP,EDU,by = 'CountryCode')

```

Answers:

```{r}
nrow(mergedDT)
mergedDT[order(-Rank)][13,.(Economy)]
```


## Question 4
What is the average GDP ranking for the "High income: OECD" and "High income: nonOECD" group?


```{r}
mergedDT['Income Group' == 'High income: OECD', lapply(.SD,mean),.SDcols = c('Rank'),by = 'Income Group']

```

## Question 5
First, you need to install and load the package 'dplyr' if you have not done so.

```{r}
breaks <- quantile(mergedDT[, Rank], probs = seq(0, 1, 0.2), na.rm = TRUE)
mergedDT$quantileGDP <- cut(mergedDT[, Rank], breaks = breaks)
mergedDT[`Income Group` == "Lower middle income", .N, by = c("Income Group", "quantileGDP")]

```
